--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
colorlinks: yes
mathspec: yes
tables: yes
graphics: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

```{r,include=FALSE}
library(dplyr)
```


# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

\[
\begin{array}{rcll}
p(\boldsymbol{\theta}|Y)  & =  & \displaystyle \frac{p(\boldsymbol{\theta},Y)}{p(Y)}
& \mbox{ [条件概率定义]}
\\[4pt]
& = & \displaystyle \frac{p(Y|\boldsymbol{\theta}) p(\boldsymbol{\theta})}{p(Y)}
& \mbox{ [链式法则]}
\\[4pt]
& = & \displaystyle \frac{p(Y|\boldsymbol{\theta})p(\boldsymbol{\theta})}{\int_{\Theta}p(Y,\boldsymbol{\theta})d\boldsymbol{\theta}}
& \mbox{ [全概率公式]}
\\[4pt]
& = & \displaystyle \frac{p(Y|\boldsymbol{\theta})p(\boldsymbol{\theta})}{\int_{\Theta}p(Y|\boldsymbol{\theta})p(\boldsymbol{\theta})d\boldsymbol{\theta}}
& \mbox{ [链式法则]}
\\[4pt]
& \propto & \displaystyle p(Y|\boldsymbol{\theta})p(\boldsymbol{\theta})
& \mbox{ [Y 是固定的]}
\end{array}
\]

The **bookdown** package can be installed from CRAN or Github:


```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

插入横线，续表的中文化

```{r kable,eval=knitr::is_latex_output()}
library(kableExtra)
db <- mtcars[, 1:7]
db2 <- cbind(rownames(db), db)
colnames(db2) <- c("Methods", rep(c("Bias", "RMSE"), 3), "")

kable(db2,
  format = "latex", booktabs = TRUE, escape = T, row.names = F,
  longtable = T, caption = "第1种类型的统计表格样式"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "repeat_header"),
    full_width = F, position = "center"
  ) %>%
  add_header_above(c(" ",
    "$\\\\sigma^2$" = 2, "$\\\\phi$" = 2,
    "$\\\\tau^2$" = 2, "$r=\\\\delta/\\\\phi$" = 1
  ), escape = F) %>%
  footnote(
    general_title = "注：", title_format = "italic", threeparttable = T,
    general = "* 星号表示的内容很长很长很长很长很长长长长长长长长长长长长长长长长长"
  )
```

`threeparttable = TRUE` 处理超长的注解标记，`add_header_above` 函数内的 `escape = F` 用来处理数学公式，`longtable = T` 表格很长时需要分页，因此使用续表

```{r kable-comp1,eval=knitr::is_latex_output()}
# 造一些数据
collapse_rows_dt <- expand.grid(
  Country = sprintf("Country with a long name %s", c("A", "B")),
  State = sprintf("State %s", c("a", "b")),
  City = sprintf("City %s", c("1", "2")),
  District = sprintf("District %s", c("1", "2"))
) %>%
  arrange(Country, State, City) %>%
  mutate_all(as.character) %>%
  mutate(
    C1 = rnorm(n()),
    C2 = rnorm(n())
  )
row_group_label_fonts <- list(
  list(bold = T, italic = T),
  list(bold = F, italic = F)
)

kable(collapse_rows_dt, "latex", longtable = TRUE,
  booktabs = T, align = "c", linesep = "",
  caption = "第2种类型的统计表格样式"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "repeat_header"),
    full_width = F, position = "center"
  ) %>% 
  column_spec(1, bold = T) %>%
  collapse_rows(1:3,
    latex_hline = "custom", custom_latex_hline = 1:3,
    row_group_label_position = "stack",
    row_group_label_fonts = row_group_label_fonts
  )
```

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

软件信息

```{r}
xfun::session_info(packages = c("rmarkdown","bookdown","kableExtra"),
                   dependencies = FALSE)
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
