--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

\[
\begin{array}{rcll}
p(\boldsymbol{\theta}|Y)  & =  & \displaystyle \frac{p(\boldsymbol{\theta},Y)}{p(Y)}
& \mbox{ [条件概率定义]}
\\[4pt]
& = & \displaystyle \frac{p(Y|\boldsymbol{\theta}) p(\boldsymbol{\theta})}{p(Y)}
& \mbox{ [链式法则]}
\\[4pt]
& = & \displaystyle \frac{p(Y|\boldsymbol{\theta})p(\boldsymbol{\theta})}{\int_{\Theta}p(Y,\boldsymbol{\theta})d\boldsymbol{\theta}}
& \mbox{ [全概率公式]}
\\[4pt]
& = & \displaystyle \frac{p(Y|\boldsymbol{\theta})p(\boldsymbol{\theta})}{\int_{\Theta}p(Y|\boldsymbol{\theta})p(\boldsymbol{\theta})d\boldsymbol{\theta}}
& \mbox{ [链式法则]}
\\[4pt]
& \propto & \displaystyle p(Y|\boldsymbol{\theta})p(\boldsymbol{\theta})
& \mbox{ [Y 是固定的]}
\end{array}
\]

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

软件信息

```{r}
xfun::session_info(packages = c("rmarkdown","bookdown"))
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
